---
title: "Notes on Organizing functions with S3 methods"
output: html_notebook
---

What if you have a general data wrangling procedure, that works for all your 
projects, but you need it customized for different variants? 
In other words, this procedure basically applies to all of your projects, but it 
is somewhat different, small things you want to change?

You make an s3 object that defines your project. 

```{r}
#create_project is a function that takes a project_name and some options, and 
#uses the structure function, which returns the given object with further 
#attributes set.
create_project <- function(project_name, options){
    project <- structure(
        list(
            project_name = project_name,
               
            # Note that you can wrap all project 
            # specific params into an options list 
            # and unpack it later in the S3 methods.
        	options = options
        ),
      
        # class name is simply the project_name, you 
        # can also assign additonal parent classes to
        # set up an inheritance structure, which is 
        # particularly useful if you have layers of 
        # projects that follow one generic procedure
       
        # E.g., class = c(project_name, "my_project")
        # all projects are also "my_project"
        class = project_name
    )
    return(project)
}

create_project("yo", options = 1)
```

R has a simple generic function mechanism which can be used for 
object-oriented style.

Method dispatch uses the class of the first argument to the generic.

UseMethod takes a generic and an object. So here process_data is the generic, 
and obj is the object.
```{r}
process_data <- function(obj, data){
    UseMethod("process_data", obj)
}
```

You can also create a default method that works for all projects
```{r}
process_data.default <- function(obj, data){
    # do something that applies to every project
    return(data)
}
```

Question: 
```{r}
process_data.my_project <- function(obj, data) {
  return(data)
}
```

Project specific s3 methods
```{r}
process_data.project_alpha <- function(obj, data) {
  options <- obj$options
  NextMethod()
}
```

If a function calls UseMethod("fun"), and it is applied to an object with class
attributes c("first", "second"), the system searches for a function called 
fun.first, and then applies it to the object. If that is not found, then it 
tries to find fun.second. If that is not found, it tries to find fun.default. If
that is not found, an error results. 

```{r}
run_data_process <- function(name, options, data){
       
  #create a project
    project <- create_project(name, options)
  #run the process_data func.
	processed_data <- process_data(
        project, 
        data = data
    )
    return(processed_data)
}
   
# execute!
alpha_processed <- run_data_process(
    "alpha", list(alpha = "good"), 
    'alpha_data'
)
beta_processed <- run_data_process(
    "beta", list(beta = "better"), 
    beta_data
)
```


#Closures
```{r}

df <- data.frame(replicate(6, sample(c(1:10, -99), 6, replace = TRUE)))
mis <- function(na_value) {
  function(x) {
    x[x == na_value] <- NA
    x
  }
}
mis99 <- mis(-99)

df[] <- lapply(df, mis99)

map(df, c(mode, median), na.rm = T)
```

